---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gfonts

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

> Download 'Google' fonts and generate CSS to use in 'rmarkdown' documents and 'shiny' applications. Some popular fonts are included and ready to use.


## Installation

You can install the development version from [GitHub](https://github.com/) with:

```r
# install.packages("devtools")
devtools::install_github("dreamRs/gfonts")
```


## Download a font to use it locally

This is a basic example which shows you how to solve a common problem:

```{r example}
library(gfonts)
## basic example code
```



## Related packages

* Package [`googlefontR`](https://github.com/timelyportfolio/googlefontR) provides helper functions to ease the use of Google Fonts with R.
* Package [`showtext`](https://github.com/yixuan/showtext) makes it easy to use various types of fonts (TrueType, OpenType, Type 1, web fonts, etc.) in R graphs.


