---
title: "Included fonts"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{included-fonts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(gfonts)
```



## Roboto

```{r}
use_pkg_gfont("roboto", selector = ".example-roboto")
```

<div class="example-roboto">
<p>abcdefghijklmnopqrstuvwxyz</p>
<p>ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
<p style="font-weight: bold;">abcdefghijklmnopqrstuvwxyz</p>
<p style="font-weight: bold;">ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
<p style="font-style: italic;">abcdefghijklmnopqrstuvwxyz</p>
<p style="font-style: italic;">ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
</div>


## Open sans

```{r}
use_pkg_gfont("open-sans", selector = ".example-open-sans")
```

<div class="example-open-sans">
<p>abcdefghijklmnopqrstuvwxyz</p>
<p>ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
<p style="font-weight: bold;">abcdefghijklmnopqrstuvwxyz</p>
<p style="font-weight: bold;">ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
<p style="font-style: italic;">abcdefghijklmnopqrstuvwxyz</p>
<p style="font-style: italic;">ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
</div>


## Lato

```{r}
use_pkg_gfont("lato", selector = ".example-lato")
```

<div class="example-lato">
<p>abcdefghijklmnopqrstuvwxyz</p>
<p>ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
<p style="font-weight: bold;">abcdefghijklmnopqrstuvwxyz</p>
<p style="font-weight: bold;">ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
<p style="font-style: italic;">abcdefghijklmnopqrstuvwxyz</p>
<p style="font-style: italic;">ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
</div>



## Montserrat

```{r}
use_pkg_gfont("montserrat", selector = ".example-montserrat")
```

<div class="example-montserrat">
<p>abcdefghijklmnopqrstuvwxyz</p>
<p>ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
<p style="font-weight: bold;">abcdefghijklmnopqrstuvwxyz</p>
<p style="font-weight: bold;">ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
<p style="font-style: italic;">abcdefghijklmnopqrstuvwxyz</p>
<p style="font-style: italic;">ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
</div>


## Alegreya

```{r}
use_pkg_gfont("alegreya", selector = ".example-alegreya")
```

<div class="example-alegreya">
<p>abcdefghijklmnopqrstuvwxyz</p>
<p>ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
<p style="font-weight: bold;">abcdefghijklmnopqrstuvwxyz</p>
<p style="font-weight: bold;">ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
<p style="font-style: italic;">abcdefghijklmnopqrstuvwxyz</p>
<p style="font-style: italic;">ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
</div>



## Nunito sans

```{r}
use_pkg_gfont("nunito-sans", selector = ".example-nunito-sans")
```

<div class="example-nunito-sans">
<p>abcdefghijklmnopqrstuvwxyz</p>
<p>ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
<p style="font-weight: bold;">abcdefghijklmnopqrstuvwxyz</p>
<p style="font-weight: bold;">ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
<p style="font-style: italic;">abcdefghijklmnopqrstuvwxyz</p>
<p style="font-style: italic;">ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
</div>



## Baloo

```{r}
use_pkg_gfont("baloo", selector = ".example-baloo")
```

<div class="example-baloo">
<p>abcdefghijklmnopqrstuvwxyz</p>
<p>ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
<p style="font-weight: bold;">abcdefghijklmnopqrstuvwxyz</p>
<p style="font-weight: bold;">ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
<p style="font-style: italic;">abcdefghijklmnopqrstuvwxyz</p>
<p style="font-style: italic;">ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
</div>



## Happy monkey

```{r}
use_pkg_gfont("happy-monkey", selector = ".example-happy-monkey")
```

<div class="example-happy-monkey">
<p>abcdefghijklmnopqrstuvwxyz</p>
<p>ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
<p style="font-weight: bold;">abcdefghijklmnopqrstuvwxyz</p>
<p style="font-weight: bold;">ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
<p style="font-style: italic;">abcdefghijklmnopqrstuvwxyz</p>
<p style="font-style: italic;">ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
</div>



## Henny Penny

```{r}
use_pkg_gfont("henny-penny", selector = ".example-henny-penny")
```

<div class="example-henny-penny">
<p>abcdefghijklmnopqrstuvwxyz</p>
<p>ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
<p style="font-weight: bold;">abcdefghijklmnopqrstuvwxyz</p>
<p style="font-weight: bold;">ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
<p style="font-style: italic;">abcdefghijklmnopqrstuvwxyz</p>
<p style="font-style: italic;">ABCDEFGHIJKLMNOPQRSTUVWXYZ</p>
</div>






